Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-26 CAV 2025 TODO/valabstraction.tex
fix

The crucial factor in such an approach is to {\em select} few opened ReLU nodes in $X$ which are the most important for the accuracy. An extreme strategy was adopted in \cite{DivideAndSlide}, where only ReLU nodes of the immediate previous layer can be opened, and the measure to choose ReLU $a$ when computing the bounds for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$. 
To obtain a more accurate measure, that 
%can also scale to deeper layers and 
is not limited to open nodes from the immediate previous layer, 
{\color{blue} we invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:}

@@

\begin{proposition}
	\label{LP}
	{\color{blue} The LP relaxation of (\ref{eq11}) is equivalent with the triangular abstraction 	(\ref{eq:deeppoly}).}
\end{proposition}

@@

\begin{proof}
	Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$.
The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediatly equivalent with $\hat{x} \geq \ReLU(x)$.

>>>>

The crucial factor in such an approach is to {\em select} few opened ReLU nodes in $X$ which are the most important for the accuracy. An extreme strategy was adopted in \cite{DivideAndSlide}, where only ReLU nodes of the immediate previous layer can be opened, and the measure to choose ReLU $a$ when computing the bounds for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$. 
To obtain a more accurate measure, that 
%can also scale to deeper layers and 
is not limited to open nodes from the immediate previous layer, 
{\color{blue} we invoke a folklore result \cite{alessandro} on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:}

@@

\begin{proposition}
	\label{LP}
	The LP relaxation of (\ref{eq11}) is equivalent with the triangular abstraction 	(\ref{eq:deeppoly}).
\end{proposition}

@@

\begin{proof}
	Consider an unstable neuron $n$, that is $\LB(n) < 0 < \UB(n)$.
The lower bound on $\hat{x}$ is simple, as $\hat{x} \geq 0 \wedge \hat{x} \geq x$ is immediately equivalent with $\hat{x} \geq \ReLU(x)$.
